---
title: "Combine"
author: "Siming Yan"
date:   "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    theme: spacelab
    keep_md: true
    toc: yes
    toc_float: true
    highlight: haddock
    
---

<html>
<style> 
div.bgm { background-color:#e6fff0; border-radius: 7px; padding: 10px;} 
.ans {
  color: purple;
  font-weight: bold;
}
#main { 
    color: #2cb061; 
}
</style>

<div class = "bgm">

<ul id="main">


```{r setup, echo=FALSE, cache=FALSE, include = F}
library(knitr)
library(rmdformats)

## Global options
options(max.print="75")
knitr::opts_chunk$set(
	fig.width = 7,
	message = FALSE,
	warning = FALSE,
	cache = TRUE,
	comment = NA,
	dpi = 300,
	prompt = FALSE,
	tidy = TRUE
)
opts_knit$set(width=75)
# knitr::opts_chunk$set()
options(digits=5)
options(scipen=5)
knitr::opts_chunk$set(warning = F, message=F)

```

### set
 
```{r setup2, include=FALSE}

library(knitr)
library(dplyr)
library(tidyr)
library(lubridate)
library(scales)
library(stargazer)
library(tidyverse)
# library(car)
library(formatR)
# library(plm)
# library(lfe)
library(data.table)
# library(mlogit)
# library(lmtest) #for coeftest() and bptest().
# library(broom) #for glance() and tidy()
# library(RCurl)# For the robust SE method 1
# library(sandwich)
library(texreg) 
library(mice) #check NA
# library(MatchIt)
library(ggthemes)
library(RColorBrewer)
library(readxl)
library(openxlsx)
library(zoo)
library(pinyin)

library(kableExtra)

```

```{r functions, warning=F, message=F, include = F}
kbt <- function(...){
  knitr::kable(..., format.args = list(big.mark = ',', scientific = F)) %>%
    kableExtra::kable_styling(c("striped", "hover", "condensed"),
                               full_width = F,
                               position = "center",
                               row_label_position = "c") %>%
   row_spec(0, bold = T, color = "white", background = "#004d1f")
}

gpt <- function(...){
  ggplot2::ggplot(...) + 
    theme_minimal() +
    theme(plot.title = element_text(face = "bold", size = 14, hjust = 0.5),
      plot.subtitle = element_text(face = "italic", size = 12, hjust = 0.5), 
      axis.text.x = element_text(angle = 0, hjust = 0.5))
}

stg <- function(...){
  stargazer::stargazer(..., 
          type = "text",
          # style = "qje",
          # title = "daily_kwh ~ post:encouraged|customer_id + no.bill|0|customer_id",
          keep.stat = c("n", "ser"),
          digits = 5)
}
```


#--------------------------------------------

## 1. data_area
```{r}
#-------------------------------------------
# read city air data,
df <- read.csv("./data/pp_data.csv")

areadata <- read.xlsx("./data/电厂名称.xlsx")
# which(is.na(areadata))
areadata <- areadata[-1,2:3]
names(areadata) <- c("plant", "area")
#--------------------------------------------
areadata2 <- read.xlsx("./data/area_lack.xlsx", colNames = T, startRow = 2) %>% na.omit()
areadata2 <- areadata2[ ,-1]
names(areadata2) <- c("plant", "area")
areadata <- rbind(areadata, areadata2)
remove(areadata2)


areadata$plant <- gsub("^\\d{1,3}[kK][vV]", "",
                         areadata$plant)

# df <- df[order(areadata$plant), ]
areadata$plant <- gsub("光伏电站", "光伏", areadata$plant)
 
areadata$plant <- gsub("忻州|晋城|运城|大同|太原|阳泉|晋中|临汾|朔州|长治|吕梁","", areadata$plant)


areadata$plant <- gsub("右玉圣水塘", "圣水塘风电场", areadata$plant)
```


```{r}
pp_data <- merge(df, areadata, by = "plant", all = T, incomparables = T, no.dups = T)

pp_data <- pp_data %>% distinct(pp_data$plant, pp_data$year, pp_data$month, .keep_all = T)

# for (i in pp_data$area){
#   if (is.na(i) == TRUE){
#     i = "undefined"
#   }
# }
# 
# pp_data %>% filter(area == "undefined")
pp_data <- pp_data[!is.na(pp_data$complete), ]

#--------------------------------------------
# only keep city names, not county.
pp_data$area2 <- substr(pp_data$area, 0, 3)

remove(ppdata)
pp_data %>% names
pp_data <- select(pp_data, -c("pp_data$plant","pp_data$year","pp_data$month", "X"))

```

<!-- ##### modified 7.21 -->
```{r}
##--------------------------------------------
# check city names:
pp_data$area2 <- gsub("忻州原", "xinzhou", pp_data$area2)
# pp_data %>% group_by(area2) %>% summarise(n())
pp_data <- pp_data[ , !names(pp_data) %in% "X"]
```


```{r}
# change city names to english names

pp_data$area3 <- pp_data$area2 %>% py(sep = "", dic = pydic(method = 'toneless', dic = "pinyin2"))
# chinese charachter convert to english.

pp_data$area3 <- gsub("shi", "", pp_data$area3)
pp_data$area3 <- gsub("lvliang", "luliang", pp_data$area3)
#--------------------------------------------

# pp_data %>% group_by(area3) %>% summarise(n())
 
```



<!-- #-------------------------------------------- -->
#--------------------------------------------
## 2. write data.
```{r }
#去除县市名称

# pp_data <- pp_data[, !names(pp_data) %in% c("area", "area2")]
pp_data <- pp_data[!is.na(pp_data$complete),]
# md.pattern(pp_data)
# pp_data <- read.csv("./data/pp_data_real.csv")
```

## 3, pinyin and wind_water_light_gas

```{r }
# library(pinyin)
# library(tidyverse)
# pp_data %>% summary
pp_data$plant_1 <- pp_data$plant %>% py(sep = "", dic = pydic(method = 'toneless', dic = "pinyin2"))
#--------------------------------------------

wind_index <- grep("风电", pp_data$plant)
pp_data$wind <- {}
pp_data$wind <- "0"

# pp_data$wind %>% str
for (i in wind_index){
  pp_data$wind[i] <- "1"
}
# write.csv(pp_data, file = "./data/pp_data_real.csv")
#--------------------------------------------


water_index <- grep("水电", pp_data$plant)
pp_data$water <- {}
pp_data$water <- "0"

# pp_data$wind %>% str
for (i in water_index){
  pp_data$water[i] <- "1"
}

#--------------------------------------------
light_index <- grep("光伏", pp_data$plant)
pp_data$light <- {}
pp_data$light <- "0"

# pp_data$wind %>% str
for (i in light_index){
  pp_data$light[i] <- "1"
}


#--------------------------------------------
fire_index <- c(1:12360)[-which(c(1:12360) %in% c(light_index, wind_index, water_index))]
pp_data$fire <- {}
pp_data$fire <- "0"
# 
# (fire_index %>% length)+(light_index %>% length)+(water_index %>% length)+(wind_index %>% length())

for (i in fire_index){
  pp_data$fire[i] <- "1"
}
#--------------------------------------------
# pp_data <- pp_data[, -which(names(pp_data) %in% c("area_2"))]
# names(pp_data)[(length(names(pp_data))-3):length(names(pp_data))] 
names(pp_data)[(length(names(pp_data))-3):length(names(pp_data))]  = c("wind", "Hydro", "photovoltaic", "Fossil-fuel")
# Hydroelectricity
```

## 4.write data (8.21)

```{r writewrite!}
pp_data <- pp_data %>% select(-c(designed_capacity, area2))
# write.csv(pp_data, file = "./data/pp_data_real.csv")
#--------------------------------------------

```

## 5. modification

```{r}

pp_freq <- pp_data$parent_company %>% table %>% as.data.frame()

df_freq <- pp_freq[order(pp_freq$Freq, decreasing = T),]
# order(Freq)

#--------------------------------------------

pp_data <- mutate(pp_data, 
                  big_five = ifelse(grepl("华能集团公司|国家电投集团公司|国电集团公司|大唐集团公司|中国华电集团|神华集团|国家能源集团|国家电投集团|国家电力投资集团有限公司|国家电投|中国华电集团有限公司|华电集团|大唐国际发电股份有限公司", 
                                          pp_data$parent_company) == T, "1", "0"))
#--------------------------------------------
# 
# df_tes <- pp_data_test[which(grepl("华能集团公司|国家电投集团公司|国电集团公司|大唐集团公司|中国华电集团|	
# 神华集团|国家能源集团|国家电投集团|国家电力投资集团有限公司|国家电投|中国华电集团有限公司|华电集团|大唐国际发电股份有限公司", pp_data$parent_company) == T),]

# 中国华能集团公司、中国大唐集团公司、中国华电集团公司、国家能源投资集团有限公司、国家电力投资集团公司
```

###

```{r}
pp_data[order(pp_data$year), ] %>% head(15)
which(is.na(pp_data$op_time)) %>% length
which(pp_data$parent_company == 'else') %>% length


# newdata <- mtcars[order(mpg),]
# sum((pp_data %>% filter(year == 20) %>% filter(month == 4))$complete)
# view(pp_data %>% filter(year == 20) %>% filter(month == 4))
# # duplicate alert
# which(duplicated((pp_data %>% filter(year == 20) %>% filter(month == 6))$plant) == T)
```

#--------------------------------------------
# test
```{r}
# duplicated()
pp_data$dup <- paste0(pp_data$year, pp_data$month, pp_data$plant, pp_data$complete)
pp_data <- pp_data[!duplicated(pp_data$dup), ]
pp_data <- select(pp_data, -"dup")
write.csv(pp_data, file = "./data/pp_data_real.csv")
```


#--------------------------------------------

<!-- #-------------------------------------------- -->
 
 


#--------------------------------------------
#--------------------------------------------
#--------------------------------------------


## 65. combine pollution_data
```{r}
pp_data %>% str
air_data_final %>% str
pp_data %>% group_by(year) %>% summarise(n())
air_data_final %>% group_by(year) %>% summarise(n())

pp_data$area3
air_data_final$area3
air_data_final <- read.csv("./data/air_data_final.csv")
dada <- merge(pp_data, air_data_final, by = c("year", "month", "area3"), all = T)
dada <- dada[!dada$plant %>% is.na() == T,]
```

#--------------------------------------------





## 66. writedown pollution*plant datas

```{r write#存1储}
# write.csv(dada, file = "./data/plant_air_data.csv")
```





#--------------------------------------------
## 98. plots1

```{r}
xingneng <- dada %>% filter(grepl("兴能..", dada$plant) == T)
str(xingneng)

# xingneng$yearmonth <- as.Date(with(xingneng, paste(year, month, sep = "-")), "y-m")
# xingneng %>% view

xingneng$yearmont <- as.yearmon(paste(xingneng$year, xingneng$month), "%y%m")

```

```{r}
# plt_xingneng <- xingneng %>% group_by(plant)
xingneng$yearmont <- xingneng$yearmont %>% as.Date()

vline = sort(xingneng$yearmont)[c(3, 25, 50, 73)]
gpt(xingneng)+
  aes(x = yearmont, y = complete, color = plant) + 
  geom_line() + 
  geom_point() +
  scale_x_date(date_breaks="month", labels = date_format("%y-%m")) +
  theme(axis.text.x = element_text(angle = 35, hjust = .5)) +
  geom_text(data = xingneng, 
            aes(x = yearmont, y = complete, label = complete),
            position = position_dodge(width = 3.7),
            vjust = -1,
            angle = -25,
            size = 4.5) +
  geom_vline(xintercept = vline, col = 2, lty = 2)
```


## 99. plots

```{r}
dada_plt_cty_plnt <- dada %>% group_by(area3) %>% summarise(n())
gpt(dada_plt_cty_plnt) +
  geom_bar(aes(x = area3, weight = `n()`))  +
  theme(axis.text.x = element_text(angle = 25, hjust = .6)) + 
  labs(title  = "Power-plant count by city",
       x = "city",
       y = "count") +
  geom_text(data = dada_plt_cty_plnt,
            aes(x = area3,
                y = `n()`,
                label=`n()`),
            vjust = -0.2)
```


```{r gpt_area_func}
gpt_area <- function(in_data, in_y, in_times){
  gpt(in_data) +
  geom_point(aes(x = area3, 
               y = in_times*in_y), 
           alpha = I(.8)) +
  geom_line(aes(x = area3, 
               y = in_times*in_y,
               group = 1)) +
  geom_bar(aes(x = area3, 
               weight = `n()`),
               alpha = I(.3)) +
  theme(axis.text.x = element_text(angle = 25, hjust = .6)) +
    geom_text(data = dada_plt_cty_plnt,
            aes(x = area3,
                y = `n()`,
                label=`n()`),
            vjust = -0.2)
}


```


```{r pm25, warning=FALSE, message=FALSE}
# dada$mean.pm25.
str(dada)
#  ________________________
 
# '------------------------'


# dada_plt_cty_air <- dada %>% group_by(area3) %>%
#   summarise(mean(mean.pm25.)) %>% 
#   merge(dada_plt_cty_plnt, by = "area3") %>% ungroup
dada_plt_cty_air <- aggregate(mean.pm25.~area3, data= dada, mean) %>% 
  merge(dada_plt_cty_plnt, by = "area3")

gpt_area(dada_plt_cty_air, dada_plt_cty_air$`mean.pm25.`, 7) +
    labs(title  = "Air_pm25 of city(sum all 3 years), plant count",
       x = "city",
       y = "count")

  
```

```{r pm10, warning=FALSE, message=F}
# dada$mean.pm10.
dada_plt_cty_air2 <- aggregate(mean.pm10.~area3, data= dada, mean) %>% 
  merge(dada_plt_cty_plnt, by = "area3") %>% ungroup

gpt_area(dada_plt_cty_air2, dada_plt_cty_air2$`mean.pm10.`, 7) +
  geom_text(data = dada_plt_cty_plnt,
            aes(x = area3,
                y = `n()`,
                label=`n()`),
            vjust = -0.2) +
    labs(title  = "Air_pm10 of city(sum all 3 years), plant count",
       x = "city",
       y = "count")
  
```

```{r So2, warning=FALSE, message=F}
# dada$mean.pm10.
dada_plt_cty_air3 <- dada %>% group_by(area3) %>%
  summarise(mean(mean.so2.)) %>% 
  merge(dada_plt_cty_plnt, by = "area3") %>% ungroup

gpt_area(dada_plt_cty_air3, dada_plt_cty_air3$`mean(mean.so2.)`, 22) +
  geom_text(data = dada_plt_cty_plnt,
            aes(x = area3,
                y = `n()`,
                label=`n()`),
            vjust = -0.2) +
    labs(title  = "Air_so2 of city(sum all 3 years), plant count",
       x = "city",
       y = "count")
  
```


```{r rmv_na_or16 complete}
# for (i in dada$complete){
#   if (i %>% is.na() == TRUE){
#   print()
#  }
#  }
dada <- dada[!is.na(dada$complete),]

comp_m_city <- dada %>% 
  group_by(area3, year) %>% 
  summarise(sum(complete))

comp_m_city <- comp_m_city[!comp_m_city$year == 16,]

# gpt_area(comp_m_city, comp_m_city$`sum(complete)`)
```


```{r}
comp_m_city$year <- as.factor(comp_m_city$year)

pow_com_city_year_plt <- gpt(comp_m_city) +
  geom_point(aes(x = area3, 
               y = `sum(complete)`,
               color = year), 
           alpha = I(.8)) +
  geom_line(aes(x = area3, 
               y = `sum(complete)`,
               color = year,
               group = year)) +
  theme(axis.text.x = element_text(angle = 25, hjust = .6)) +
    labs(title  = "Plant complete power generated of city(3 years)",
       x = "city",
       y = "count") 
  # scale_color_discrete(palette = "Set1")
pow_com_city_year_plt
```


```{r pm25a}
year_pm25_city <- dada %>% 
  group_by(area3, year) %>% 
  summarise(mean(mean.pm25.))

year_pm25_city <- year_pm25_city[!year_pm25_city$year == 16,]

# gpt_area(comp_m_city, comp_m_city$`sum(complete)`)
```



```{r}
# pm25 plot with city complete power generated
pow_com_city_year_plt + 
  geom_line(data = year_pm25_city,
           aes(x = area3, 
               y = year_pm25_city$`mean(mean.pm25.)`, group = year,
               color = as.factor(year)),
           alpha = I(.9), linetype = 3) +
    labs(subtitle = "air_quality_pm25",
       x = "city",
       y = "count") 
```

From plot above we can easily observe that due to policy change and technology advance, air quality of pm 2.5 is not correlated to power generated at city level, but i have not exclude wind power, solar power plant by now.



```{r}
dada$yearmon <- paste0(dada$year,dada$month) %>% as.factor()
library(lfe)
fit1 <- felm(mean.pm25. ~ complete|yearmon + area3|0|area3, data = dada)
fit1 %>% summary
```

similar results obtained from regression output, fixed-effect include "year month + city",
clustered at "city" level.



<span style="font-size:13px;color:#8B30BB;">end of the piece</span>

